---
title: "PSES 2018 @ TBS"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(scales)
```

```{r}
```

## Load Data

Read all PSES 2017 subsets and combine them into a single PSES 2017 table.
```{r load data}
ss1 <- read_csv("datasets//2017_PSES_SAFF_Subset-1_Sous-ensemble-1.csv", na = "9999")
ss2 <- read_csv("datasets//2017_PSES_SAFF_Subset-2_Sous-ensemble-2.csv", na = "9999")
ss3 <- read_csv("datasets//2017_PSES_SAFF_Subset-3_Sous-ensemble-3.csv", na = "9999")
ss4 <- read_csv("datasets//2017_PSES_SAFF_Subset-4_Sous-ensemble-4.csv", na = "9999")
ss5 <- read_csv("datasets//2017_PSES_SAFF_Subset-5_Sous-ensemble-5.csv", na = "9999")
mapQ <- read_csv("datasets//Question_Mappings.csv")
mapDemQ <- read.csv("datasets//Demo_Question_Mappings.csv")

pses2017 <- bind_rows(ss1,ss2,ss3,ss4,ss5)
```

## Process Data

### Select data

Select only TBS data. TBS's LEVEL1ID is 26 and LEVEL2ID == "0" includes aggregate Public Service data.
```{r}
TBS.df <- subset(pses2017, LEVEL1ID %in% c("26","0") & SURVEYR == 2017,
                select=c(LEVEL1ID,SURVEYR,BYCOND,DESCRIP_E,DESCRIP_F,
                         QUESTION,TITLE_E,TITLE_F,POSITIVE,NEUTRAL,NEGATIVE,SCORE100,ANSCOUNT))
```

### Merge Data from Other Sources

Create question subsections, themes and demographic categories using mappping tables I have created. Note that they only contain TBS-relevant mapping data. Addtional work would need to be done to generalize them form use by other departments.

```{r}
# Create question subsections by extracting the leading character from QUESTION, e.g., "A" from "A_Q01"
TBS.df$QSection <- substr(ss.df$QUESTION,0,1)
TBS.df$QSection <- factor(ss.df$QSection)

# Create demographic question subsections by extracting the leading code from BYCOND preceding "=" 
# Also replace NA with "TBS"
TBS.df$BYCOND[TBS.df$DESCRIP_E == "Treasury Board of Canada Secretariat"] <- "TBS"
TBS.df$BYCOND[TBS.df$DESCRIP_E == "Public Service"] <- "PS" 
TBS.df$DemoQ <- word(TBS.df$BYCOND, 1, sep = " =")

# Add question and demographic sections from mapping tables
TBS.df <- merge(ss.df, mapQ, by = "QUESTION")
TBS.df <- merge(ss.df, mapDemQ, by = "BYCOND")

```

### Aggregate Data

Since there are over a hundred questions in the survey, they can't all be be displayed on a single page (or even 2!). Consequently, we need a way to summarize them into fewer categories. We have the option of sections or themes, which we derived earlier.

Here, I've gone with themes, as they were used as the basis for Statistics Canada's suplied analysis. (Makes you wonder why the theme data isn't provided in the dataset or the documentation.)

These will be plotted on the vertical axis.
```{r}
# Aggregate by demographic and question theme
TBSagg.df <- aggregate(data = ss.df, cbind(ANSCOUNT,SCORE100,NEGATIVE,NEUTRAL,POSITIVE) ~ 
                            LEVEL1ID + QSubTheme_E + QSubTheme_F + DemoQ + DemQ_E + DemQ_F + BYCOND +
                            DESCRIP_E + DESCRIP_F + SURVEYR, mean)

# Calculate proportions for each TBS demographic group and append to the descriptors (DesProp_E and DesProp_F).
# We will want the description fields with TBS-only proportions to be common to both PS and TBS data
# so we can graph them together. This is why we output to another dataframe (TBSprops.df), which we merge below.
TBSprops.df <- TBSagg.df %>%
  filter(LEVEL1ID == "26") %>%
  group_by(DemoQ, DESCRIP_E) %>%
  mutate(ngrp = sum(ANSCOUNT)) %>%
  group_by(DemoQ) %>%
  mutate(npop = sum(ANSCOUNT)) %>%
  ungroup() %>%
  mutate(prop = ngrp/npop) %>%
  mutate(DesProp_E = paste0(DESCRIP_E, " (", round((prop*100),0),"%)")) %>%
  mutate(DesProp_F = paste0(DESCRIP_F, " (", round((prop*100),0),"%)")) %>%
  distinct(DESCRIP_E, DesProp_E, DesProp_F) %>%
  # Here, we're just adding an empty line for the Public Service - percentages are only relevant for TBS.
  rbind(c("Public Service","Public Service","Fonction publique"))

# Add demographic sections from mapping tables (the "mapDemQ" lookup table is based on TBS data
# and will therefore filter out all PS data not shared by TBS, e.g., non-TBS occupational groups)
TBSagg.df <- merge(TBSagg.df, mapDemQ, by = "BYCOND")

# As mentioned above, we merge  the TBSprops.df dataframe to the orginal dataframe to keep descriptors consistent
# between PS and tBS data. The preceding merge with "mapDemQ" has already stripped away non-shared descriptions.
TBSagg.df <- merge(TBSagg.df, TBSprops.df, by = "DESCRIP_E")

# Transform the positive-neutral-negative crosstab into a list 
TBSagg.df <- gather(TBSagg.df, key = "sentiment", value = "prop", NEGATIVE,NEUTRAL,POSITIVE)
```

## Select Demographic Categories

We have now processed the totality of TBS data. Wenow need to slect what demograhpic categories to display. Again, space is a consideration. 

These will be plotted on the horizontal axis.
```{r}
# Order SubThemes by least to most negative  
subThemeOrder <- TBSagg.df %>%
  filter(BYCOND == "M_Q103A = 011" & variable == "NEGATIVE") %>%
  arrange(value)
TBSagg.df <- TBSagg.df %>%
  mutate(QSubTheme_E = factor(QSubTheme_E, unique(subThemeOrder$QSubTheme_E))) %>%
  mutate(QSubTheme_F = factor(QSubTheme_F, unique(subThemeOrder$QSubTheme_F)))

# Select demographic groups to plot: AS & CR groups, plus PS and TBS summary columns for comparison
TBSagg.df <- subset(TBSagg.df, BYCOND %in% c("M_Q103A = 011","M_Q103A = 023","TBS","PS") | 
                         DemQ_E %in% c("AS","CR")) 

# Order occupational levels by overall group and then ascending level using the existing "OrderKey" column
# from the mapDemQ lookup table.
TBSagg.df <- TBSagg.df %>% 
  arrange(OrderKey) %>%
  mutate(DesProp_E = factor(DesProp_E, unique(DesProp_E))) %>%
  mutate(DesProp_F = factor(DesProp_F, unique(DesProp_F)))

# Make PS and TBS overall the first levels (don't forget the percentages appended to the descriptors!)
TBSagg.df$DesProp_E <- fct_relevel(TBSagg.df$DesProp_E, c("Public Service",
                                                                "Treasury Board of Canada Secretariat (100%)"))
TBSagg.df$DesProp_F <- fct_relevel(TBSagg.df$DesProp_F, c("Fonction publique",
                                                                "Secrétariat du Conseil du Trésor du Canada (100%)"))
```


```{r}
# LABELS
#---------------
#English captions and labels
expl_E <- "Each cell of this chart displays the proportion of responses for a particular question theme and demographic category. The bars over each column represent the average value for this question theme for TBS. Question themes are sorted from least negative to most negative (the red column) for the AS group at TBS."
expl_E <- paste0(strwrap(expl_E, 100), sep="", collapse="\n")
ttl_E <- "PSES@TBS 2017 - AS & CR Groups"
cap_E <- "2017 Public Service Employee Survey Open Datasets"
file_E <- paste0(ttl_E,".pdf")
TBSagg.df$variable_E <- mapvalues(TBSagg.df$variable, 
                                     c("NEGATIVE","NEUTRAL","POSITIVE"),
                                     c("Negative","Neutral","Positive"))
PNN_E.lbls <- c("Negative" = "Negative", "Neutral" = "Neutral", "Positive" = "Positive", 
                "Public Service" ="PS", "Treasury Board of Canada Secretariat (100%)" ="TBS")
PNN_E.clrs <- c("Negative" = "#CD202C", "Neutral" = "#63CECA", "Positive" = "#CCDC00", 
                "Treasury Board of Canada Secretariat (100%)" = "#d1e7ee", "Public Service" = "#fabcb3")

#French Captions and labels
expl_F <- "Chaque cellule de ce graphique affiche la proportion de réponses pour un thème de question et une catégorie démographique particuliers. Les barres sur chaque colonne représentent la valeur moyenne pour ce thème de question pour le SCT. Les thèmes de la question sont triés du moins négatif au plus négatif (la colonne rouge) pour le groupe AS du SCT."
expl_F <- paste0(strwrap(expl_F, 100), sep="", collapse="\n")
ttl_F <- "SAFF@SCT 2017 - Groupes AS & CR" 
cap_F <- "Ensemble de données ouvertes du Sondage auprès des fonctionnaires fédéraux de 2017"
file_F <- paste0(ttl_F,".pdf")
TBSagg.df$variable_F <- mapvalues(TBSagg.df$variable, 
                                     c("NEGATIVE","NEUTRAL","POSITIVE"),
                                     c("Négatif","Neutre","Positif"))
PNN_F.lbls <- c("Négatif" = "Négatif", "Neutre" = "Neutre", "Positif" = "Positif",
                "Fonction publique" = "FP","Secrétariat du Conseil du Trésor du Canada (100%)" = "SCT")
PNN_F.clrs <- c("Négatif" = "#CD202C", "Neutre" = "#63CECA", "Positif" = "#CCDC00",
                "Secrétariat du Conseil du Trésor du Canada (100%)" = "#d1e7ee", "Fonction publique" = "#fabcb3")
#---------------
```


```{r}
# Create separate TBS and PS dataframes
TBSagg_noPS.df <- filter(TBSagg.df, LEVEL1ID == "26" | BYCOND == "PS")
TBSagg_PS.df <- filter(TBSagg.df, LEVEL1ID == "0" | BYCOND == "TBS")

# Create TBS mean column to allow each small multiple to be compared to the TBS mean via geom_errorbar
TBSagg_noPS.df <- TBSagg_noPS.df %>%
  arrange(QSubTheme_E, variable, DESCRIP_E) %>%
  group_by(QSubTheme_E, variable) %>%
  mutate(TBSmean = value[2]) %>%
  mutate(TBSmeanDiff = value - TBSmean)

# Compute PS overall means to compare to the PS, TBS and Sector data

PSoverall <- TBSagg_PS.df %>%
  filter(BYCOND %in% c("PS","TBS")) %>%
  arrange(QSubTheme_E, variable, OrderKey) %>%
  group_by(QSubTheme_E, variable) %>%
  mutate(value = value[1])

PSdetail <- filter(TBSagg_PS.df, !(BYCOND %in% c("PS","TBS")))

TBSagg_PS.df <- bind_rows(PSoverall, PSdetail)
```


```{r}
# Define a plotting function for all subthemes. Inputs are language (E or F) and graph dimensions in inches.
plotIS <- function(language, wdth = 10, hght = 8, textSize = 9) {
  
  if (language == "E") {
    TBSagg_noPS.df$variable_lang <- TBSagg_noPS.df$variable_E
    TBSagg_noPS.df$DESCRIP_lang <- TBSagg_noPS.df$DesProp_E
    TBSagg_noPS.df$QSubTheme_lang <- TBSagg_noPS.df$QSubTheme_E
    TBSagg_noPS.df$DemQ_lang <- TBSagg_noPS.df$DemQ_E
    TBSagg_PS.df$variable_lang <- TBSagg_PS.df$variable_E
    TBSagg_PS.df$DESCRIP_lang <- TBSagg_PS.df$DesProp_E
    TBSagg_PS.df$QSubTheme_lang <- TBSagg_PS.df$QSubTheme_E
    TBSagg_PS.df$DemQ_lang <- TBSagg_PS.df$DemQ_E
    PNN_lang.clrs <- PNN_E.clrs
    PNN_lang.lbls <- PNN_E.lbls
    expl_lang <- expl_E
    ttl_lang <- ttl_E
    cap_lang <- cap_E
    file_lang <- file_E
    TBSmean_lang <- "TBS mean across all levels"
    PSmean_lang <- "PS mean by level"
    TBS_lang <- "Treasury Board of Canada Secretariat (100%)"
    PS_lang <- "Public Service"
  } else if (language == "F") {
    TBSagg_noPS.df$variable_lang <- TBSagg_noPS.df$variable_F
    TBSagg_noPS.df$DESCRIP_lang <- TBSagg_noPS.df$DesProp_F
    TBSagg_noPS.df$QSubTheme_lang <- TBSagg_noPS.df$QSubTheme_F
    TBSagg_noPS.df$DemQ_lang <- TBSagg_noPS.df$DemQ_F
    TBSagg_PS.df$variable_lang <- TBSagg_PS.df$variable_F
    TBSagg_PS.df$DESCRIP_lang <- TBSagg_PS.df$DesProp_F
    TBSagg_PS.df$QSubTheme_lang <- TBSagg_PS.df$QSubTheme_F
    TBSagg_PS.df$DemQ_lang <- TBSagg_PS.df$DemQ_F
    PNN_lang.clrs <- PNN_F.clrs
    PNN_lang.lbls <- PNN_F.lbls
    expl_lang <- expl_F
    ttl_lang <- ttl_F
    cap_lang <- cap_F
    file_lang <- file_F
    TBSmean_lang <- "moyenne SCT pour tous les niveaux"
    PSmean_lang <- "moyenne FP par niveau"
    TBS_lang <- "Secrétariat du Conseil du Trésor du Canada (100%)"
    PS_lang <- "Fonction publique"
  } else {
    return("Invalid language selection. Choose E (English) or F (French).")
  }
  
  ggplot(data=TBSagg_noPS.df, aes(x=variable_lang, y=value, fill = variable_lang)) +
    geom_rect(data = subset(TBSagg_noPS.df,DESCRIP_lang == TBS_lang),
              aes(fill = DESCRIP_lang),xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf,alpha = 0.3) +
    geom_rect(data = subset(TBSagg_noPS.df,DESCRIP_lang == PS_lang),
              aes(fill = DESCRIP_lang),xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf,alpha = 0.3) +
    geom_rect(data = subset(TBSagg_noPS.df,DemoQ %in% c("M_Q103A")),
              fill = "grey80",xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf,alpha = 0.3) +
    geom_rect(data = subset(TBSagg_noPS.df,TBSmeanDiff >= 8 & variable == "NEGATIVE"),
              fill = "#e3f800",xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf,alpha = 0.8) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = PNN_lang.clrs, labels = PNN_lang.lbls) +
    geom_errorbar(aes(ymax=TBSmean, ymin=TBSmean, linetype = TBSmean_lang), colour = "grey20") +
    geom_errorbar(data = TBSagg_PS.df, 
                  aes(ymax=value, ymin=value, linetype = PSmean_lang), colour = "grey20") +
    scale_linetype_manual(values=c("dotted", "solid")) +
    ggtitle(ttl_lang) +
    labs(fill = "Response type", 
         subtitle = expl_lang,
         caption = cap_lang) +
    facet_grid(QSubTheme_lang ~ DESCRIP_lang, switch = "y", scales = "free_y",
               labeller = labeller(DESCRIP_lang = label_wrap_gen(8), QSubTheme_lang = label_wrap_gen(15)))  +
    theme(plot.title = element_text(size = 20, hjust = 0, colour = "grey40"),
          plot.subtitle = element_text(face = "bold", size = textSize, colour = "grey40"),
          plot.caption = element_text(face = "italic", size = textSize, colour = "grey45"),
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks = element_blank(),
          panel.background = element_rect(fill = "grey95"),
          panel.grid = element_blank(),
          panel.spacing.y = unit(0, "mm"),
          panel.spacing.x = unit(0.5, "mm"),
          strip.text.y = element_text(angle = 180, size = textSize, colour = "grey40", inherit.blank = FALSE),
          strip.text.x = element_text(angle = 0, size = textSize, colour = "grey40", inherit.blank = FALSE),
          strip.background = element_blank(),
          legend.text = element_text(size = textSize, colour = "grey45"),
          legend.title = element_blank(),
          legend.position = "bottom")
  
  ggsave(file_lang, height = hght, width = wdth)
  
  return()
  
}
```


```{r}
plotIS("E", 8, 13.5, 8)
plotIS("F", 8, 13.5, 8)
```


```{r}
```