---
title: "Harassment differences between EXs and non-EXs"
output: html_notebook
---

```{r setup}
source("pses2018.R")

library(tidyverse)
library(cowplot)
```

```{r}
topic_map <- tribble(
  ~QUESTION, ~topic, ~item,
  "Q48", "", "Harassment",
  "Q49a", "Source", "Co-workers",
  "Q49b", "Source", "Authority over me",
  "Q49c", "Source", "Working for me",
  "Q49d", "Source", "Custodial responsbility",
  "Q49e", "Source", "From other departments",
  "Q49f", "Source", "Members of the public",
  "Q49g", "Source", "Other source",
  "Q50a", "Nature", "Aggressive behaviour",
  "Q50b", "Nature", "Excessive control",
  "Q50c", "Nature", "Excluded or ignored",
  "Q50d", "Nature", "Humiliation",
  "Q50e", "Nature", "Interference / resources withheld",
  "Q50f", "Nature", "Offensive remark",
  "Q50g", "Nature", "Personal attack",
  "Q50h", "Nature", "Physical violence",
  "Q50i", "Nature", "Sexual comment or gesture",
  "Q50j", "Nature", "Threat",
  "Q50k", "Nature", "Unfair treatment",
  "Q50l", "Nature", "Yelling / shouting",
  "Q50m", "Nature", "Other nature",
  "Q51a", "Action", "Discuss with manager",
  "Q51b", "Action", "Discuss with source",
  "Q51c", "Action", "Contacted an HR advisor",
  "Q51d", "Action", "Contacted a union rep",
  "Q51e", "Action", "Used informal conflict resolution",
  "Q51f", "Action", "Filed a grievance or complaint",
  "Q51g", "Action", "Resolved informally by victim",
  "Q51h", "Action", "Other action",
  "Q51i", "Action", "No action taken",
  "Q52a", "Reason for no action", "Issue resolved",
  "Q52b", "Reason for no action", "Not serious enough",
  "Q52c", "Reason for no action", "Behaviour stopped",
  "Q52d", "Reason for no action", "Individual apologized",
  "Q52e", "Reason for no action", "Managemnt intervened",
  "Q52f", "Reason for no action", "Source left",
  "Q52g", "Reason for no action", "Victim changed jobs",
  "Q52h", "Reason for no action", "Did not know what to do",
  "Q52i", "Reason for no action", "Too distraught",
  "Q52j", "Reason for no action", "Concerns about process",
  "Q52k", "Reason for no action", "Advised against complaint",
  "Q52l", "Reason for no action", "Afraid of reprisal",
  "Q52m", "Reason for no action", "Threatened by someone",
  "Q52n", "Reason for no action", "Believed it would not work",
  "Q52o", "Reason for no action", "Still intend to take action",
  "Q52p", "Reason for no action", "Other reason"
)
```

```{r, fig.width=7, fig.height=10}
har_data <- pses2018 %>% 
  filter(LEVEL1ID == 26,
         SURVEYR == 2018,
         DemoQ == "Q78A",
         SUBINDICATORID == 12) %>% 
  mutate(exec = ifelse(DESCRIP_E == "EX", "EX", "non-EX"),
         n_agree = AGREE/100 * ANSCOUNT) %>%
  group_by(QUESTION, TITLE_E,exec) %>% 
  summarise(n_agree = sum(n_agree),
            anscount = sum(ANSCOUNT),
            prop_agree = (n_agree / anscount * 100) %>% round(0)) %>% 
  ungroup() %>%
  full_join(topic_map, by = "QUESTION") %>% 
  mutate(sub_question = QUESTION,
         QUESTION = str_sub(QUESTION,1,3)) %>% 
  select(QUESTION,sub_question,everything()) %>% 
  arrange(desc(exec), QUESTION, prop_agree) %>% 
  mutate(item = fct_inorder(item),
         topic = fct_inorder(topic))

ggplot(data = filter(har_data, !is.na(topic)), aes(x = item, y = prop_agree)) +
  geom_col(fill = "#3095B4") +
  geom_text(aes(label = paste0(prop_agree,"%")), vjust = 0.5, hjust = -0.2) +
  coord_flip() +
  scale_y_continuous(breaks = c(0, 50, 100), limits = c(0,100)) +
  facet_grid(rows = vars(topic), cols = vars(exec), scales = "free_y", space = "free") +
  theme_minimal_vgrid() +
  labs(title = "Experiences of harassment") +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank())

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
